Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/overview.tex
minor

\begin{theorem}
  Consider an execution of \texttt{qs1} with a randomly permuted input
  of $n$ keys and performing $m$ executions of \texttt{qs2} with the
  result of \texttt{qs1}.  The total run-time for this computation is
  $\Theta(n\log{n} + m\log{n})$ in expectation.
\end{theorem}
\begin{proof}
  We use a few standard facts.  We note first that \texttt{qs1} is
  isomorphic to a quick-sort algorithm, which builds a binary search
  tree instead of combining the returned results in a list.  The
  run-time for \texttt{qs1} is thus (expected) $O(n\log{n})$. 
%
  The depth of the tree generated by \texttt{qs1} is isomorphic to the
    depth of a run of the quickselect algorithm or equivalently to the
    span of a parallel implementation of the quicksort algorithm, both
    of which are known to be (expected) $\Theta(\log{n})$.
%
    By inspection of \texttt{qs2}, we can see that the algorithm takes
    time proportional to the depth of the binary search tree, which is
    $\Theta(\log{n})$. Consider now a random variable for each of the
    $m$ invocations of \texttt{qs2}, each of which takes expected
    $\Theta(\log{n})$ time.  Since the total time is the sum of these
    random variables and since the expectation of the sum is sum of
    the expectations of the random variables, the bound follows.
\end{proof}

>>>>

\begin{theorem}
  Consider an execution of \texttt{qs1} with a randomly permuted input
  of $n$ keys and performing $m$ executions of \texttt{qs2} with the
  result of \texttt{qs1}.  The total run-time for this computation is
  $\Theta(n\log{n} + m\log{n})$ in expectation.
\end{theorem}
\begin{proof}
  We use a few standard facts.  We note first that \texttt{qs1} is
  isomorphic to a quick-sort algorithm but builds a binary search tree
  instead of combining the returned results in a list.  The run-time
  for \texttt{qs1} is thus (expected) $\Theta(n\log{n})$.
%
  The depth of the tree generated by \texttt{qs1} is isomorphic to the
    depth of a run of the quickselect algorithm or equivalently to the
    span of a parallel implementation of the quicksort algorithm, both
    of which are known to be (expected) $\Theta(\log{n})$.
%
    By inspection of \texttt{qs2}, we can see that the algorithm takes
    time proportional to the depth of the binary search tree, which is
    $\Theta(\log{n})$. Consider now a random variable for each of the
    $m$ invocations of \texttt{qs2}, each of which takes expected
    $\Theta(\log{n})$ time.  Since the total time is the sum of these
    random variables and since the expectation of the sum is sum of
    the expectations of the random variables, the bound follows.
\end{proof}
